KidsAIR: Main analysis

### 2021-03-24 lrti_tracking.Rmd
small analysis updates for paper tables

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  select(area, home_winter_id, treatment_assigned) %>% 
  distinct(area, home_winter_id, .keep_all = TRUE)

@@

fig1_stats <- lrti_final_data %>% 
  left_join(health_exposure_data_sampling_day, by = c("area", "home_winter_id")) %>% 
  filter(winter_id != 0) %>% 
  group_by(area, winter_id, treatment_assigned) %>% 
  filter(!is.na(person_time_possible)) %>% 
  mutate(child_weeks_obs = as.numeric(person_time_possible),
         child_weeks_obs = sum(child_weeks_obs)/7) %>% 
  distinct(area, winter_id, treatment_assigned, .keep_all = TRUE) %>% 
  select(area, winter_id, treatment_assigned, child_weeks_obs)

>>>>

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  dplyr::select(area, home_winter_id, treatment_assigned) %>% 
  distinct(area, home_winter_id, .keep_all = TRUE)

@@

fig1_stats <- lrti_final_data %>% 
  left_join(health_exposure_data_sampling_day, by = c("area", "home_winter_id")) %>% 
  filter(winter_id != 0) %>% 
  group_by(treatment_assigned) %>% 
  filter(!is.na(person_time_possible)) %>% 
  mutate(child_weeks_obs = as.numeric(person_time_possible),
         child_weeks_obs = sum(child_weeks_obs)/7) %>% 
  distinct(treatment_assigned, .keep_all = TRUE) %>% 
  dplyr::select(treatment_assigned, child_weeks_obs)

### 2021-03-24 main_analysis_final.Rmd
small analysis updates for paper tables

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 26 Feb 2021"
output: pdf_document
---

@@

@@

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_noak_tidy,
                              itt_income_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy,
                              itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  theme_bw() +  
  geom_hline(yintercept =  1) +
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

@@

@@

#table(model.frame(itt_results_int)$treatment_assigned)
#((exp(-.418)-1)*100)
```

@@

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT PM at-home", "ITT no AK", "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "% difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

#nobs(er_results)
#isSingular(er_results)
```

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 24 March 2021"
output: pdf_document
---

@@

obs <- analysis_data %>% 
  filter(!is.na(lrti_events_di_total)) %>% 
  filter(!is.na(child_age)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  filter(!is.na(residents_smoke)) %>%
  group_by(residents_smoke, treatment_assigned) %>% 
  count()
obs

@@

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_noak_tidy,
                              itt_income_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  theme_bw() +  
  geom_hline(yintercept =  1) +
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

  new_model_data <- model_data %>% 
    #distinct(area, child_id_num, .keep_all = T) %>% 
    rename(int_var = interaction_var)

@@

obs <- analysis_data_winter1 %>% 
  distinct(area, child_id_num, .keep_all = T) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  filter(!is.na(child_age)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  filter(!is.na(home_sqft_2level)) %>%
  group_by(home_sqft_2level, treatment_assigned) %>% 
  count()
obs

@@

#((exp(-.418)-1)*100)
```

@@

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT PM at-home", "ITT no AK", "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM2.5 outcome") +
  labs(y = "% difference in PM2.5 \n compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + 
                          amb_temp_lrti + amb_pm_lrti + residents_smoke +
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

#nobs(er_results)
#table(model.frame(er_results)$residents_smoke)

#isSingular(er_results)
```
